\bf Service Chain Placement in SDNs \thanks{ A preliminary version appeared in the 3rd International Workshop on Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017. Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2019-03-14 src/response.tex

\documentclass[11pt]{article}

\usepackage{amsmath,latexsym,amssymb} 
\usepackage{fullpage,ifthen}
\usepackage{color,soul,colordvi}
\usepackage{mdwlist,paralist}

%\renewcommand{\baselinestretch}{1.02}

%\parskip=\smallskipamount

\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\set}[1]{\left\{ #1 \right\}}

\newcommand{\eps}{\varepsilon}

\newcommand{\calC}{\mathcal{C}}
\newcommand{\sigmad}{\sigma_{\$}}

\newcommand{\ans}[1]{\begin{quotation}{\noindent \sl {#1}}\end{quotation}}

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
\newcommand{\ben}[1]{\sethlcolor{green}\hl{Ben: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\textbf{Service Chain Placement in SDN} \\
  {\Large Response to Reviewers: Submission DA10028}}

\author{Gilad Kutiel \and Dror Rawitz}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the time that was spent on reviewing our
paper and for their thoughtful comments.  The paper was revised
according to these comments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\medskip

\section*{Response to Review \#1}

\begin{enumerate}

\item \textbf{Comment}: In Sec.~5.1 for the randomized algorithm it is
  claimed in p.11 row 29, that ``... each edge $e$ in $E$ is found on
  a simple path between two neighborly nodes $v_e$ and $v_{e'}$, in
  which all internal vertices are in $V \ N$''.  $N$ denotes the set
  of neighborly nodes. Here it is not clear for me, how this is ensured
  if, e.g, $G$ is a tree and $N$ is the set of internal nodes with
  degree greater than two.  It needs more explanation. The approach
  described in Sec 5.2 eliminates this problem.

\item[] \textbf{Response}: Before Section 5.1 we observe, that
  w.l.o.g., we may focus on vertices that are located on a path from
  $s$ to $t$.  It follows that each such vertex has degree at least
  $2$.
%
  In Section~5.1 we now consider edges that are located between $s$ or
  $t$ and a neighborly vertex.

\item \textbf{Comment}: In proof of Lemma 1, p.10 row 16: $\leq \eps
  c_{\max} / n \cdot \sum_\alpha (c(\alpha,f(\alpha))\cdot \eps
  c_{max} / n + 1)$ $\longrightarrow$ $\leq \eps c_{\max} / n \cdot
  \sum_\alpha (c(\alpha,f(\alpha))\cdot n / (\eps c_{max}) + 1)$

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: In p.~15 row 24: ``... for $v_1 \neq v_2$
  ...'' I suppose, it must be ``... for $v_1 \neq v_2$ or $v_1 = v_2 =
  t$ ...''

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: In p.~15 row 34: ``$\beta_i \preceq \alpha_i$
  or $\beta_i = \zeta_i$''.  What does then $\text{COST}^i(\zeta_i \to
  \alpha_i)$ mean in row 26?

\item[] \textbf{Response}: First, we changed $i$ to $j$, since $i$ is
  used for the layer number.

  If $\beta_j = \zeta_j$, then $\textsc{cost}^j_{v_j}(\zeta_j \to
  \alpha_j) = 0$.  We added a footnote about this issue.

\item \textbf{Comment}: In p.~15 after row 37, to my opinion, an
  additional item should be inserted: $v_1 \neq v_2$ or $v_1 = v_2 =
  t$.

\item[] \textbf{Response}: First, this is handled by the response to
  comment 3.  Also, $v_1$ and $v_2$ are not variables over which the
  minimum is taken.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

\section*{Response to Review \#2}

We corrected all typos in the list.

\subsection*{Additional references/explanations}

\begin{enumerate}

\item \textbf{Comment}: Please expand the explanations for Figure 1,
  the introductory example. For a first-time reader, it is not
  intuitive.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please expand the explanation at the end of
  Theorem 2 a bit.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please provide a reference to the FPTAS for
  the MINIMUM KNAPSACK problem.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please expand the explanation at the end of
  Theorem 5 a bit and/or provide a citation.

\item[] \textbf{Response}: The proof was extended.

\item \textbf{Comment}: Please provide a reference for the block-cut
  tree and expand the explanation a bit.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please expand the proof of Theorem 4, it is a
  bit short at the moment (maybe it is obvious and I don't see it?)

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please define internal vertex disjoint on page
  12.

\item[] \textbf{Response}: The definition was added in a footnote.

\item \textbf{Comment}: Please expand the explanation at the end of
  Theorem 9, I don't see it right now.

\item[] \textbf{Response}: The explanations before and after Theorem 9
  were extended.

\item \textbf{Comment}: reference 5 has been extended at TOCS 2018
  (On-Line Path Computation and Function Placement in SDNs)
  https://link.springer.com/article/10.1007/s00224-018-9863-4

\item[] \textbf{Response}: A citation was added.

\item \textbf{Comment}: reference 8 has been extended for the
  unordered case (LATIN 2018 (Walking Through Waypoints):
  https://link.springer.com/chapter/10.1007\%2F978-3-319-77404-6\_4),
  and the ordered case (CCR 2018 (Charting the Algorithmic Complexity
  of Waypoint Routing):
  https://dl.acm.org/citation.cfm?doid=3211852.3211859, and IFIP
  Networking 2018 (Waypoint Routing in Special Networks):
  https://files.ifi.uzh.ch/stiller/IFIP\%20Networking\%202018-Proceedings.pdf).

\item[] \textsc{Response}: The paper are mentioned in the intro.

\item \textbf{Comment}: Lastly, reference 15 has been extended at IFIP
  Networking 2018 as well (see
  https://files.ifi.uzh.ch/stiller/IFIP\%20Networking\%202018-Proceedings.pdf). The
  same authors also presented some prior work in Computer Networks
  (https://www.sciencedirect.com/science/article/abs/pii/S138912861500359X?via\%3Dihub)
  which should be briefly discussed

\item[] \textsc{Response}: The paper are mentioned in the intro.

\item \textbf{Comment}: Please include a small conclusion with open
  questions at the end. For example, how about walks instead of paths?
  How about multiple concurrent requests?

\item[] \text{Response}: Added.

\end{enumerate}

\end{document}

### 2019-03-14 src/chain.tex
dror

\nonstopmode
\documentclass[preprint,12pt]{elsarticle}

\usepackage{amsmath,amssymb,mathtools,amsthm}
% \usepackage{fullpage}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{stmaryrd}

\usepackage[final]{hyperref}
\usepackage{subfig}

@@

\journal{Discrete Applied Mathematics}

@@

% \newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

@@

% FIX
\newcommand{\fix}[1]{{\color{violet}\textbf{#1}}}

\begin{document}
\begin{frontmatter}

\title{Service Chain Placement in SDNs\tnoteref{t1}}
\tnotetext[t1]{
A preliminary version appeared in the 3rd International Workshop on
Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017.
%
Research supported in part by Network Programming (Neptune)
Consortium, Israel.
}

\author{Gilad Kutiel}
\ead{gkutiel@cs.technion.ac.il}
\address{Department of Computer Science, Technion, Haifa 32000, Israel.}

\author{Dror Rawitz\fnref{f1}}
\ead{dror.rawitz@biu.ac.il}
\address{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.}
\fntext[f1]{Partially supported by the Israel Science Foundation (grant no.~497/14).}

@@

\begin{keyword}
approximation algorithms \sep randomized algorithms \sep network function virtualization \sep resource allocation \sep service chaining \sep software defined network.

\end{keyword}

\end{frontmatter}

@@

Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
admission control and placement of service chains, where each chain is
associated with a source-destination pair and is supposed to be routed
via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
instantiations, but each node has a limited capacity that bounds the
number of requests it may service.
%
They presented an $O(\log \ell)$-competitive algorithm for the problem
of maximizing the number of serviced chains, assuming that capacities
are $\Omega(\log \ell)$.
%at least logarithmic in $\ell$.
It is also shown that this ratio is asymptotically optimal even for
randomized online algorithms.  APX-hardness results for the offline
version of the problem were also presented.
%
Rost and Schmid~\cite{RostSchmid16} considered variant of this
problem, where each node can host a subset of the VNFs.  In addition,
each VNF has a demand and each VNF-node pair has a capacity, and in a
feasible solution the total demand for each pair is bounded by the
capacity.  They considered two goals: maximum profit and minimum
resource cost and gave bicriteria approximation algorithms which are
based on LP-rounding for several special cases.
%
\fix{Sahhaf et al.~\cite{SAHHAF2015492} studied a generalization of the Virtual Network Embedding
Problem where each network function can be decomposed into multiple network function graphs.
They proposed two novel approaches to use service
decompositions at the time of service embedding (i) an
ILP-based algorithm that finds an optimal embedding and (ii) a heuristic-based algorithm to cop with the scalability issues of the first algorithm.}

Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
computation and VNF placement.  They considered compound requests that
arrive in an online manner.  Each request is a flow with a
specification of routing and VNF requirements which is represented by
a directed acyclic graph (DAG) whose vertices are VNFs.  Each VNF can
be performed by a specified subset of servers in the system.  Upon
arrival of a request, the algorithm either rejects the request or
accepts it with a specific routing and VNF assignment, under given
server capacity constraints.  Each request has a benefit that is
gained if it is accepted, and the goal is to maximize the total
benefit gained by accepted requests.
%
Even, Medina, and Patt-Shamir~\cite{EMP16} proposed an algorithm that
copes with requests with unknown duration without preemption by using
a third response, which is refer to as “stand by”, whose competitive
ratio is $O(\log (knb_{\max}))$, where $n$ is the number of nodes,
$b_{\max}$ is an upper bound on a request benefit per time unit, and
$k$ is the maximum number of VNFs of any service chain.  This
performance guarantee holds for the case where the processing of any
request in any possible service chain is never more than
$O(1/(k \log (nk)))$ fraction of the capacity of any network
component.
%
Even, Rost, and Schmid~\cite{ERS16} presented a randomized
approximation algorithm for the same problem that computes
$(1-\eps)$-approximate placements if the demand of any processing
request in any possible service chain is never more than an
$O(\eps^2/\log n)$ fraction of the capacity of any network component.

Foerster, Parham and Schmid~\cite{FPS17} considered the
\textsc{Bidirectional Waypoint Routing} problem, where the input
consists of a graph $G = (V,E)$ with edge weights and capacities, a
source $s$, a destination $t$, and a subset of the vertices $W$.  A
feasible solution is a route from $s$ to $t$ that visits the vertices
in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
according to the given order.  The goal is to find a minimum weight
solution.
%
Foerster et al.~\cite{FPS17} showed that the unordered
problem has no PTAS, assuming P$\neq$NP and gave a
$1.53$-approximation algorithm.  They also presented polynomial time
algorithms for special cases.
%
As for the ordered variant, they showed that feasible routes can be
computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
that the problem is NP-hard and gave a polynomial time algorithm for
cactus graphs with constant link capacities.

@@

\subsection{Model}
%
An instance of the \scplong (\scp) problem is composed of three
components, a physical network, a virtual specification, and placement
costs:
\begin{description}
\item[Physical network:]
%
  The physical network is a graph $G = (V,E)$.  Each node $v \in V$
  has a non-negative processing capacity $p(v)$, and each directed
  edge $e \in E$ has a non-negative bandwidth capacity $b(e)$.
%
  % Without loss of generality, we assume that $p(s) = p(t) = 0$.

@@

\item[Virtual specification:]
%
  The description of a request for a service chain consists of a
  physical source $s \in V$, a physical destination $t \in V$, and a
  directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
%
  The DAG $\calG$ has a source node $\sigma \in \calV$ and a
  destination $\tau \in \calV$. Each node $\alpha \in \calV$ represent
  a VNF that has a processing demand $p(\alpha)$.
%
\fix{Without loss of generality, we assume that $p(s) = p(t) = p(\sigma) = p(\tau) =
  0$}.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.

@@

\begin{figure}[]
\centering
\scalebox{0.9}{
\input{fig-embedding}
}
\caption{\fix{
  An example of an \scp instance and a solution.
  The left DAG represents the collection of alternative service chains as requested by the client.
  Each node of this graph represent a single service and the number written inside the node is the processing demand of this service.
  The value on the arcs are the minimum bandwidth required to transmit the output of one service to the next service.
  \\
  The right DAG represents a physical network. 
  The numbers on the nodes represent processing capacities and the number on the arcs represent the available bandwidth.
  \\
  The blue, dashed, arcs represent the chosen service chain and a physical route respectively, and the dotted, purple, arrows show a placement of this service chain into the physical route.
}}
\label{fig:solution}
\end{figure}

@@

The \scp instance can be computed in polynomial time.
%
\fix{
Note that any service chain is of the form $\sigma, \gamma_1, \dots, \gamma_n, \tau$ where $\gamma_i \in \{\alpha_i, \beta_i\}$. 
This implies that given a service chain, the sum of its cost and its total processing demand equals to $\sum_i a_i$ and thus (as forced by the processing capacity of $v$), $\set{a_1, \ldots, a_n} \in \textsc{Partition}$ if and only if there exists a solution whose cost is $\half \sum_i a_i$.
}
\end{proof}

\begin{figure}[]
  \centering
\scalebox{1}{
  \input{fig-reduction}
}
\caption{The specification defined in the proof of Theorem~\ref{thm:simple}.}
\label{fig:simple}
\end{figure}

@@

\begin{figure}[]
\centering
\scalebox{.75}{
\input{fig-reduction2}
}
\caption{A reduction from a partition instance $a_1, \ldots, a_n$.
  The cost function enforces each $\alpha_i$ to be placed either in
  $v_i^-$ or in $v_i^+$.  In the former case this placement incurs no
  cost but additional latency of $a_i$, in the later case there will
  be additional $a_i$ cost with zero latency.}
\label{fig:reduction2}
\end{figure}

@@

In this section we present an FPTAS for \scp in DAGs for general
costs, namely without the assumption that costs are polynomially
bounded.  
\fix{
We use similar techniques as in the  FPTAS for the
\textsc{Minimum Knapsack} problem~\cite{islam2009approximation}.
}

@@

\begin{lemma}
\label{lemma:guess}
$c(f') \leq (1+\eps)c(f)$.
\end{lemma}
\begin{proof}
We have that
\begin{align*}
c(f')
%&
=    \sum_{\alpha} c(\alpha,f'(\alpha)) %\\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f'(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot
     \sum_{\alpha}
       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max}} + 1} \\
%& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
& =    c(f) + \eps c_{\max} \\
& \leq (1+\eps) c(f)
~,
\end{align*}
where the second inequality is due to the optimally of $f'$ with
respect to $c'$.
\end{proof}

@@

\begin{theorem}
\label{thm:fptas}
There exists an FPTAS for \scp in DAGs.
\end{theorem}
\begin{proof}
Given $\eps>0$, run the dynamic programming algorithm from
Section~\ref{sub:DPL} $\abs{\calV} \cdot \abs{V}$ times, once for each
possible value of $c_{\max}$, and choose the best placement.
\fix{Since we check all the possible values of $c_{max}$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.  
The running time is polynomial in the input size and in $1/\eps$.
\end{proof}

@@

@@

\fix{We assume w.l.o.g that the physical network does not contain any leafs (beside, maybe, $s$ and $t$), otherwise, these nodes, for the purpose of our computation, can be safely removed from the network.}
Our randomized algorithm consists of $k!$ iterations of the following
two phases: an orientation phase that applies a random orientation to
the physical network, and an execution of the FPTAS for DAGs given in
Theorem~\ref{thm:fptas}.  The algorithm finds a $(1+\eps)$-approximate
placement with probability $(1-1/e)$, and the running time of the
algorithm is $O((n+t(n))k!)$, where $t(n)$ is the time it takes to
compute a placement when the physical network is a DAG.
%
As usual, one may amplify the probability of success using repetition.

The orientation phase is done as follows.  Let $N$ be the set of
neighborly vertices.  We assume without loss of generality that $N =
\set{1,\ldots,\abs{N}}$.
%
Let $\pi:N \to N$ be a random permutation.  We direct the edges
according to $\pi$.  
Observe that each edge $e \in E$ is found on a
simple path between two neighborly nodes $v_e$ and $v'_e$, in which
all internal vertices are in $V \setminus N$.  The edge $e$ is
directed towards $v_e$, if $\pi(v_e) > \pi(v'_e)$, and otherwise it is
directed towards $v'_e$.
%
Observe that when this process terminates we get a DAG, denoted by
$G_\pi$, where there is a topological order than is consistent which
$\pi$.  Figure~\ref{fig:orientation} depicts the orientation phase.
%
A na\"ive implementation of this phase would run in $O(|V||E|)$ time.

\begin{figure}[t]
\centering
\scalebox{0.9}{
  \input{fig-orientation}
}
\caption{Orientation phase: on the left is the physical network, where
  only the neighborly nodes are drawn.  The numbers represent the
  permutation and the dashed path represents a path of an optimal
  placement.  The orientated physical network is on the right.  It is
  enough that the internal ordering of the nodes on the dashed path is
  "correct" to ensure the survival of an optimal placement. }
\label{fig:orientation}
\end{figure}

@@

\fix{
A biconnected component (block) of an undirected graph is a maximal biconnected subgraph.
Any connected graph decomposes into a tree of biconnected components called the block-cut tree of the graph. The blocks are attached to each other at shared vertices called cut vertices.
Computing such a tree can be done in linear time~\cite{HopcroftTarjan73}.
}
The orientation works as follow.  
Given an undirected graph $G = (V,E)$, we first compute its block-cut tree.
%
Then on the unique path from $s$ to $t$ in the block-cut tree we
internally orient each block arbitrarily to produce a DAG.  Note that
if $B_1, \ldots, B_\ell$ are the blocks of $G$ on the path from $s$ to
$t$ then the first and last vertices with respect to each block are
known and only the order of the internal neighborly vertices in each
block is needed to be determined, thus, we can find all relevant
orientations by repeating the process above $\Pi_{i = 1}^\ell
\abs{N_i}$ times, where $N_i$ is the set of internal neighborly
vertices in $B_i$.  See Figure~\ref{fig:or2} for an example.

>>>>

%\nonstopmode
\documentclass[11pt]{article}
%\documentclass[runningheads]{llncs}

\usepackage{amsmath,amssymb,mathtools}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{xspace}
\usepackage{color,soul}
\usepackage{paralist}
\usepackage{stmaryrd}

% \usepackage[linesnumbered, ruled]{algorithm2e}

%\usepackage[final]{microtype}
\usepackage[final]{hyperref}
\usepackage{subfig}
%\usepackage{subcaption}

% DEBUG
%\usepackage{lipsum}
%\usepackage{todonotes}
%\usepackage{lineno}
%\linenumbers

% EXTRA
%\usepackage{authblk}

@@

\renewcommand{\floatpagefraction}{0.6}

\parskip = \smallskipamount

\sloppy

%\spnewtheorem{observation}{Observation}{\bfseries}{\itshape}

@@

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

@@

\begin{document}

\title{\bf Service Chain Placement in SDNs%
\thanks{%
%
A preliminary version appeared in the 3rd International Workshop on
Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017.
%
Research supported in part by Network Programming (Neptune)
Consortium, Israel.}
%
}

%\titlerunning{Service Chain Placement in SDNs}

%\author[1]{Gilad Kutiel%
%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}

%\author[2]{Dror Rawitz%
%\thanks{Partially supported by the Israel Science Foundation
%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}

%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}

\author{%
Gilad Kutiel%
\thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
{\tt\small gkutiel@cs.technion.ac.il}
\and
Dror Rawitz%
\thanks{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel. Partially supported by the Israel Science Foundation
  (grant no.~497/14). } \\
{\tt\small dror.rawitz@biu.ac.il}
}

\begin{titlepage}

\maketitle

@@

\bigskip

\noindent
\textbf{Keyworks}:
approximation algorithms,
randomized algorithms,
network function virtualization,
resource allocation,
service chaining,
software defined network.

\renewcommand{\thepage}{}
\end{titlepage}
\pagenumbering{arabic}

@@

Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
admission control and placement of service chains, where each chain is
associated with a source-destination pair and is supposed to be routed
via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
instantiations, but each node has a limited capacity that bounds the
number of requests it may service.
%
They presented an $O(\log \ell)$-competitive algorithm for the problem
of maximizing the number of serviced chains, assuming that capacities
are $\Omega(\log \ell)$.
%at least logarithmic in $\ell$.
It is also shown that this ratio is asymptotically optimal even for
randomized online algorithms.  APX-hardness results for the offline
version of the problem were also presented.
%
Sahhaf et al.~\cite{STRSCPD15} also studied placement of network
service chains.  They presented an algorithm which minimizes the cost
of the placement and is based on integer linear programming.  They
also present a heuristic in order to cope with the non-practical
running time of the first algorithm.
%
Rost and Schmid~\cite{RostSchmid16} considered variant of this
problem, where each node can host a subset of the VNFs.  In addition,
each VNF has a demand and each VNF-node pair has a capacity, and in a
feasible solution the total demand for each pair is bounded by the
capacity.  They considered two goals: maximum profit and minimum
resource cost and gave bicriteria approximation algorithms which are
based on LP-rounding for several special cases.
%
Rost and Schmid~\cite{RostSchmid18} considered a more general version
of the problem in which requests are graphs that should be placed
within the physical graph.  They provided hardness of approximation
results for this problem.

Even, Medina, and Patt-Shamir~\cite{EMP16} (see, also~\cite{EMP18})
studied online path computation and VNF placement.  They considered
compound requests that arrive in an online manner.  Each request is a
flow with a specification of routing and VNF requirements which is
represented by a directed acyclic graph (DAG) whose vertices are VNFs.
Each VNF can be performed by a specified subset of servers in the
system.  Upon arrival of a request, the algorithm either rejects the
request or accepts it with a specific routing and VNF assignment,
under given server capacity constraints.  Each request has a benefit
that is gained if it is accepted, and the goal is to maximize the
total benefit gained by accepted requests.
%
Even, Medina, and Patt-Shamir~\cite{EMP16} proposed an algorithm that
copes with requests with unknown duration without preemption by using
a third response, which is refer to as “stand by”, whose competitive
ratio is $O(\log (knb_{\max}))$, where $n$ is the number of nodes,
$b_{\max}$ is an upper bound on a request benefit per time unit, and
$k$ is the maximum number of VNFs of any service chain.  This
performance guarantee holds for the case where the processing of any
request in any possible service chain is never more than
$O(1/(k \log (nk)))$ fraction of the capacity of any network
component.
%
Even, Rost, and Schmid~\cite{ERS16} presented a randomized
approximation algorithm for the same problem that computes
$(1-\eps)$-approximate placements if the demand of any processing
request in any possible service chain is never more than an
$O(\eps^2/\log n)$ fraction of the capacity of any network component.

Foerster, Parham and Schmid~\cite{FPS17} considered the
\textsc{Bidirectional Waypoint Routing} problem, where the input
consists of a graph $G = (V,E)$ with edge weights and capacities, a
source $s$, a destination $t$, and a subset of the vertices $W$.  A
feasible solution is a route from $s$ to $t$ that visits the vertices
in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
according to the given order.  The goal is to find a minimum weight
solution.
%
Foerster et al.~\cite{FPS17} showed that the unordered
problem has no PTAS, assuming P$\neq$NP and gave a
$1.53$-approximation algorithm.  They also presented polynomial time
algorithms for special cases.
%
As for the ordered variant, they showed that feasible routes can be
computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
that the problem is NP-hard and gave a polynomial time algorithm for
cactus graphs with constant link capacities.
%
Amiri et al.~\cite{AFS18} considered the unordered case, and they
presneted a polynomial-time algorithm for graphs of bounded treewidth.
%
Amiri et al.~\cite{AFJPS18} studied the ordered case, and they
gave algorithms for special networks.
%
An overview of waypoint routing is given in ~\cite{AFJS18}.

@@

\subsection{Model}
%
An instance of the \scplong (\scp) problem is composed of three
components, a physical network, a virtual specification, and placement
costs:
\begin{description}
\item[Physical network:]
%
  The physical network is a graph $G = (V,E)$.  Each node $v \in V$
  has a non-negative processing capacity $p(v)$, and each directed
  edge $e \in E$ has a non-negative bandwidth capacity $b(e)$.
%
  Without loss of generality, we assume that $p(s) = p(t) = 0$.

@@

\item[Virtual specification:]
%
  The description of a request for a service chain consists of a
  physical source $s \in V$, a physical destination $t \in V$, and a
  directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
%
%   Without loss of generality, we assume that $p(s) = p(t) = 0$.  
%
  The DAG $\calG$ has a source node $\sigma \in \calV$ and a
  destination $\tau \in \calV$. Each node $\alpha \in \calV$ represent
  a VNF that has a processing demand $p(\alpha)$.
%
  Without loss of generality, we assume that $p(\sigma) = p(\tau) =
  0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.

@@

\begin{figure}[t]
\centering
\scalebox{0.9}{
\input{fig-embedding}
}
\caption{An example of an \scp instance and a solution.
%
The DAG on the left is the virtual DAG, and the numbers on its
vertices and edges are their demands.
%
The DAG on the right is the physical DAG, and the numbers of its
vertices and edges are their capacities.
%
The dashed blue line on the left is the chosen the chosen virtual
path, while the dashed blue line on the right is the chosen physical
path.  Dotted lines are used to represent the allocation of each set
of virtual vertices to each physical vertex along the path.
%
}
\label{fig:solution}
\end{figure}

@@

The \scp instance can be computed in polynomial time.
%
Furthermore, observe that any service chain must be of the form
$\sigma, \gamma_1, \ldots, \gamma_n, \tau$, where $\gamma_i \in
\set{\alpha_i,\beta_i}$.  By the construction, we have that the total
processing demands plus the total cost is $\sum_i a_i$.  Since $p(v) =
\half \sum_i a_i$, we have that the total cost is at least $\sum_i
a_i$.  Hence, it is not hard to verify that $\set{a_1, \ldots, a_n}
\in \textsc{Partition}$ if and only if there exists a solution whose
cost is $\half \sum_i a_i$.
\end{proof}

\begin{figure}[t]
  \centering
\scalebox{1}{
  \input{fig-reduction}
}
\caption{The specification defined in the proof of Theorem~\ref{thm:simple}.}
\label{fig:simple}
\end{figure}

@@

\begin{figure}[t]
\centering
\scalebox{.75}{
\input{fig-reduction2}
}
\caption{A reduction from a partition instance $a_1, \ldots, a_n$.
  The cost function enforces each $\alpha_i$ to be placed either in
  $v_i^-$ or in $v_i^+$.  In the former case this placement incure no
  cost but additional latency of $a_i$, in the later case there will
  be additional $a_i$ cost with zero latency.}
\label{fig:reduction2}
\end{figure}

@@

In this section we present an FPTAS for \scp in DAGs for general
costs, namely without the assumption that costs are polynomially
bounded.  Our algorithm is similar to the FPTAS for the
\textsc{Minimum Knapsack} problem (see \cite{KPP04}[Chapter 13] and
references therein).

@@

\begin{lemma}
\label{lemma:guess}
$c(f') \leq (1+\eps)c(f)$.
\end{lemma}
\begin{proof}
We have that
\begin{align*}
c(f')
%&
=    \sum_{\alpha} c(\alpha,f'(\alpha)) %\\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f'(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot
     \sum_{\alpha}
       \paren{ \frac{c(\alpha,f(\alpha))}{c_{\max}} \cdot \frac{n}{\eps} + 1} \\
%& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
& =    c(f) + \eps c_{\max} \\
& \leq (1+\eps) c(f)
~,
\end{align*}
where the second inequality is due to the optimality of $f'$ with
respect to $c'$.
\end{proof}

@@

\begin{theorem}
\label{thm:fptas}
There exists an FPTAS for \scp in DAGs.
\end{theorem}
\begin{proof}
First, observe that there are $\abs{\calV} \cdot \abs{V}$ candidates
for the value of $c_{\max}$, one for each pair of virtual function and
physical vertex.  
%
Hence, given $\eps>0$, we run the dynamic programming algorithm from
Section~\ref{sub:DPL} $\abs{\calV} \cdot \abs{V}$ times, once for each
possible value of $c_{\max}$, and choose the best placement.
%
According to Lemma~\ref{lemma:guess} the placement that was computed
for the value of $c_{\max}$ that corresponds to an optimal solution is
$(1+\eps)$-approximate.  Hence, the best placement is also
$(1+\eps)$-approximate.
%
The running time is polynomial in the input size and in $1/\eps$.
\end{proof}

@@

Before presenting our algorithms we assume without loss of generality
that each vertex in the network is found on a path from $s$ to $t$,
since otherwise it can be eliminated.  In particular, it follows that
the degree of any vertex, besides maybe $s$ and $t$, is at least $2$.
In addition this implies that the network is connected.

@@

Our randomized algorithm consists of $k!$ iterations of the following
two phases: an orientation phase that applies a random orientation to
the physical network, and an execution of the FPTAS for DAGs given in
Theorem~\ref{thm:fptas}.  The algorithm finds a $(1+\eps)$-approximate
placement with probability $(1-1/e)$, and the running time of the
algorithm is $O((n+t(n))k!)$, where $t(n)$ is the time it takes to
compute a placement when the physical network is a DAG.
%
As usual, one may amplify the probability of success using repetition.

The orientation phase is done as follows.  Let $N$ be the set of
neighborly vertices.  We assume without loss of generality that $N =
\set{1,\ldots,\abs{N}}$.
%
Let $\pi:N \to N$ be a random permutation.  Define $\pi(s) = 0$, and
$\pi(t) = N+1$.  We direct the edges according to $\pi$.
%
Observe that each edge $e \in E$ is found on a simple path between two
neighborly nodes $v_e$ and $v'_e$, between $v_e = s$ and a neighborly
node $v'_e$, or between neighborly node $v_e$ and $v_e = t$.  In this
path all internal vertices are in $V \setminus N$.  The edge $e$ is
directed towards $v_e$, if $\pi(v_e) > \pi(v'_e)$, and otherwise it is
directed towards $v'_e$.
%
Observe that when this process terminates we get a DAG, denoted by
$G_\pi$, where there is a topological order than is consistent which
$\pi$.  Figure~\ref{fig:orientation} depicts the orientation phase.
%
A na\"ive implementation of this phase would run in $O(|V||E|)$ time.

\begin{figure}[t]
\centering
\scalebox{0.9}{
  \input{fig-orientation}
}
\caption{Orientation phase: on the left is the physical network, where
  only the neighborly nodes are drawn.  The numbers represent the
  permutation and the dashed path represents a path of an optimal
  placement.  The oriented physical network is on the right.  It is
  enough that the internal ordering of the nodes on the dashed path is
  "correct" to ensure the survival of an optimal placement. }
\label{fig:orientation}
\end{figure}

@@

Given a connected graph $G$, a \emph{bi-connected component} (or a
\emph{block}) in $G$ is a maximal bi-connected subgraph of $G$.  Any
connected graph can be decomposed into bi-connected subgraphs that
form a tree called a \emph{block-cut tree}.  In this tree every vertex
is a block of $G$ and two blocks are attached if they share a vertex,
which is called a \emph{cut-vertex}.
%
Computing such a tree can be done in linear
time~\cite{HopcroftTarjan73}.

The orientation works as follow.  Given an undirected graph $G =
(V,E)$, we first compute its \emph{block-cut} tree.  Then on the
unique path from $s$ to $t$ in the block-cut tree we internally orient
each block arbitrarily to produce a DAG.
%
Note that if $B_1, \ldots, B_\ell$ are the blocks of $G$ on the path
from $s$ to $t$ then the first and last vertices with respect to each
block are known and only the order of the internal neighborly vertices
in each block is needed to be determined, thus, we can find all
relevant orientations by repeating the process above $\Pi_{i = 1}^\ell
\abs{N_i}$ times, where $N_i$ is the set of internal neighborly
vertices in $B_i$.  See Figure~\ref{fig:or2} for an example.
